### 2016-05-31 paper/reordered.tex
Bunch of small comments

Regular expressions are a nice way to formalize a set of strings, called a language.
They have nice computational properties.  The syntax for nonempty regular expressions
is given in Figure~\ref{fig:regex-syntax}.
These regular expressions have an underlying semantics, which expresses languages,
formalized in Figure~\ref{fig:regex-semantics}.

\input{fig_lens-syntax}
\input{fig_lens-alternate-alternate-semantics}
There are things called views, which allow one a different perspective on data.
Lenses are updatable views, which satisfy the get-put laws.
One can approach creating lenses that satisfy the laws through a language approach.
We focus our attentions currently on the language of bijective lenses, where the
functions between views are bijections, and inverses to each other.
We define the syntax for these bijective lenses in Figure~\ref{fig:lens-syntax}.
The semantics and typing for these lenses is defined in Figure~\ref{fig:lens-alternate-alternate-semantics}.
The semantics is only defined alongside the typing, as the functions are only
well defined when the term is well typed.

@@

\input{fig_dnf-regex-rewrites}
Because of this, instead of writing equivalences for DNF regular expressions like
exist for normal regular expressions,
instead we write rewrite rules as shown in Figure~\ref{fig:dnf-regex-rewrites}.
Intuitively, these rewrite rules correspond to breaking a regular expression
into a regular expression that encodes additional semantics.
We define these rules as rewrites that turn atoms into DNF Regular expressions,
and a rule that expresses how these rewrites can become rewrites on
the DNF regular expressions themselves.

Roughly, the Atom Sumstar rewrite corresponds to Regular Expression equivalence 8,
the Atom Unrollstar rewrite corresponds to Regular Expression equivalence 9,
and the Atom Powerstar rewrite corresponds to Regular Expression equivalence 11.
There is no rewrite corresponding to Regular Expression equivalence 10, as that
equivalence is an ambiguity introducing equivalence.
An application of Atom Sumstar corresponds to doing different things after the last time a certain event has occured, and before the last time that event occurs.
An application of Atom Unrollstar corresponds to making a different action for
the empty case of an iteration, the first case of an iteration, and all further cases of the iteration.
An application of Atom Powerstar corresponds to doing different things if the iteration
is occuring a different number of times, modulo n, for some fixed n.

>>>>

The syntax for nonempty\bcp{why not empty ones too??} regular expressions
is given in Figure~\ref{fig:regex-syntax}.
These regular expressions have an underlying semantics, which expresses languages,
formalized in Figure~\ref{fig:regex-semantics}.

\input{fig_lens-syntax}
\input{fig_lens-alternate-alternate-semantics}
We focus on the language of bijective lenses, where the
functions between views are bijections, and inverses to each other.
We define the syntax for these bijective lenses in Figure~\ref{fig:lens-syntax}.
The semantics and typing for these lenses is defined in Figure~\ref{fig:lens-alternate-alternate-semantics}.
The semantics is only defined alongside the typing, as the functions are only
well defined when the term is well typed.

@@

\input{fig_dnf-regex-rewrites}
Because of this, instead of writing equivalences for DNF regular expressions like
exist for normal regular expressions,
instead we write rewrite rules as shown in
Figure~\ref{fig:dnf-regex-rewrites}.\bcp{Don't understand what's going on here.}
Intuitively, these rewrite rules correspond to breaking a regular expression
into a regular expression that encodes additional semantics.
We define these rules as rewrites that turn atoms into DNF Regular expressions,
and a rule that expresses how these rewrites can become rewrites on
the DNF regular expressions themselves.

Roughly, the Atom Sumstar rewrite corresponds to Regular Expression equivalence 8,
the Atom Unrollstar rewrite corresponds to Regular Expression equivalence 9,
and the Atom Powerstar rewrite corresponds to Regular Expression equivalence 11.
There is no rewrite corresponding to Regular Expression equivalence 10, as that
equivalence is an ambiguity introducing equivalence.
An application of Atom Sumstar\bcp{Wrong font} corresponds to doing different things after the last time a certain event has occured, and before the last time that event occurs.
An application of Atom Unrollstar corresponds to making a different action for
the empty case of an iteration, the first case of an iteration, and all further cases of the iteration.
An application of Atom Powerstar corresponds to doing different things if the iteration
is occuring a different number of times, modulo n, for some fixed n.
